A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-11-30 02_Materials_and_Methods.Rmd
some outline ideas for materials and methods
started to work on materials and methods

Test

>>>>

The analysis code of this paper is written in the statistics programming language R [@rcoreteamLanguageEnvironmentStatistical2018] and fully reproducible: **doi**.

The dataset used for the analysis in this paper is a subset of the openly available database Radon-B [@kneiselRadonB2013]. It contains ^14^C dates from the European Bronze and Early Iron Age (2300 BC to 500 BC). Radiocarbon dating is one of the major absolute dating techniques for this period [@ramseyRadiocarbonDatingRevolutions2008] and Radon-B is a collection of more than 11,000 published dates  from around 3,500 sites from all over europe.

The first step of data preparation was to download the Radon-B dataset with the R package c14bazAAR [@schmidC14bazAARDownloadPrepare2018], which allows to access several open radiocarbon archives.

- Main steps of data preparation and grouping

- Spatial Distance

- Cultural distance

The SED is defined as:

$$d_{ij}^2 = \sum_{k = 1}^{n} (p_{ik} - p_{jk})^2$$

- $d_{ij}^2$: SED between tqo groups $i$ and $j$
- $k$: trait counter 
- $n$: number of traits in the population
- $p_{ik}$: relative frequency of the $k$th trait in group $i$
- $p_{jk}$: relative frequency of the $k$th trait in group $j$

- Simulation
